Marketing Analysis

### 2015-12-12 2_marketing_analysis/marketing_analysis.Rmd
update work

A more intuitive way when referring to the purpose of segmentation is: You can't treat every single one of your customers the same way, charge them the same price or communicate in the same benefits. But as that being said, you can't treat each and every customer individually as that will be way too costly. So a good segmentation is to find the right balance between simplifying it to make it usable and not simplifying it much so that it is still valuable.

@@

# environment setting
library(dplyr)
library(ggplot2)
library(gridExtra)
library(lubridate)
library(data.table)
setwd("/Users/ethen/Business-Analytics/3_marketing_analysis")

@@

rfm1 <- data[ , .( recency 	 = min(recency),
				   frequency  = .N, 
				   avg_amount = mean(purchase_amount) ), by = customer_id ]

# distibution
grid.arrange( ggplot( rfm1, aes( avg_amount ) ) + geom_histogram(),
			  ggplot( rfm1, aes( frequency )  ) + geom_histogram(), ncol = 2 )

>>>>

A more intuitive way when referring to the purpose of segmentation is: You can't treat every single one of your customers the same way, charge them the same price or communicate in the same benefits. But as that being said, you can't treat each and every customer individually, as that will be way too costly. So a good segmentation is to find the right balance between simplifying it to make it usable and not simplifying it much so that it is still valuable.

@@

# environment setting
library(dplyr)
library(ggplot2)
library(gridExtra)
library(lubridate)
library(data.table)
setwd("/Users/ethen/Business-Analytics/2_marketing_analysis")

@@

rfm1 <- data[ , .( recency 	  = min(recency),
				   frequency  = .N, 
				   avg_amount = mean(purchase_amount) ), by = customer_id ]
# distibution
grid.arrange( ggplot( rfm1, aes( avg_amount ) ) + geom_histogram(),
			  ggplot( rfm1, aes( frequency )  ) + geom_histogram(), ncol = 2 )
